Cluster Difference Imaging Photometric Survey. I. Light Curves of Stars in Open Clusters from TESS Sectors 6 \& 7

### 2019-08-12 paper_I/ms.tex
paper: minor

Most of these pipelines are geared towards tasks more general than our
own, and use aperture photometry.  The SPOC pipeline
produces the calibrated FFIs from raw images, processes 2 minute data,
identifies exoplanets, and produces the TESS data
products of record.  The MIT-QLP processes a subset of stars on the
FFIs, identifies exoplanets, and the affiliated TESS Science Office
alerts object of interest for ground and space-based followup.  The
\texttt{eleanor} pipeline is a user-friendly tool for
extracting light curves from the FFIs.  The team developing it is
also performing transit searches across the full set of FFIs.  The
TASOC pipeline is primarily aimed towards asteroseismology.  The
\citeauthor{oelkers_precision_2018} pipeline was aimed at broad,
all-sky variability searches, and used similar difference
imaging methods as our own.  Finally, the Padova team's effort is
developed with a similar focus towards clusters as our work, but uses
PSF subtraction to mitigate crowding.  This ecosystem
provides many opportunities for methodological improvements as light
curve products continue to be made public.

There are of course caveats and possible areas for improvement
in our own work.
One methodological point concerns the hyperparameter tuning
required by our difference imaging method (\S~\ref{subsec:tuneconvkernel}).
Within our fine-tuning experiments over different kernel box-sizes
and polynomial weightings,
we found that low-significance transit signals could be ``lost''
relative to the noise for different choices of parameters that
ideally would not affect the photometric pipeline's results.
In the longer
term, developing an image-subtraction method that marginalizes over
uncertainties of how to chose ``optimal'' kernels would be desirable.
Pixel-level image subtraction methods that omit these parameters
entirely are also worth exploring \citep{wang_pixel-level_2017}.

>>>>

Most of these pipelines are geared towards tasks more general than our
own, and use aperture photometry.  The SPOC pipeline produces the
calibrated FFIs from raw images, processes 2 minute data, identifies
exoplanets, and produces the TESS data products of record.  The
MIT-QLP processes a subset of stars on the FFIs, identifies
exoplanets, and the affiliated TESS Science Office alerts object of
interest for ground and space-based followup.  The \texttt{eleanor}
pipeline is a user-friendly tool for extracting light curves from the
FFIs.  The team developing it is also performing transit searches
across the full set of FFIs.  The TASOC pipeline is primarily aimed at
asteroseismology and variable star classification.  The
\citeauthor{oelkers_precision_2018} pipeline was aimed at broad,
all-sky variability searches, and used difference imaging methods
similar to our own.  Finally, the Padova team's effort is also
directed towards star clusters, but uses PSF subtraction to mitigate
crowding.  This ecosystem provides many opportunities for
methodological improvements as light curve products continue to be
made public.

There are of course caveats and possible areas for improvement in our
own work.  One methodological point concerns the hyperparameter tuning
required by our difference imaging method
(\S~\ref{subsec:tuneconvkernel}).  Within our fine-tuning experiments
over different kernel box-sizes and polynomial weightings, we found
that low-significance transits  could be ``lost'' to the noise for
different choices of parameters that ideally should not affect the
photometric pipeline's results.  In the longer term, developing an
image-subtraction method that marginalizes over uncertainties of how
to chose ``optimal'' kernels would be desirable.  Pixel-level image
subtraction methods that omit these parameters entirely are also worth
exploring \citep{wang_pixel-level_2017}.
